---
title: "GET YOU A KATIE"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE, echo = FALSE)
library(stringr)
library(ggplot2)
library(rJava)
library(NLP)
library(openNLP)
library(dplyr)
library(igraph)
library(networkD3)
library(knitr)
library(data.table)
library(egg)
library(gridExtra)
library(ggpubr)
library(highcharter)
library(plotly)
library(htmlwidgets)
library(tweetrmd)
library(webshot2)
library(emo)
```

#### **What is this?**

One of the most oft repeated pieces of advice for aspiring writers looking for
literary agents is to look at the acknowledgements section of novels to see
which literary agents represent the writers they admire. From there, the advice
goes, just query those agents and, with a bit of work and kismit, one day 
*you'll* be the published author whose acknowledgements people are trawling.

Okay, then!

The rest of this analysis is me taking that advice... too far? Sure I could have
read the acknowledgements, made my list of literary agents and gone about my
business, but I had more questions. And when I have questions, I do stuff with
data. (I am a novelist cum data scientist, if you recall.) 

I created a dataset consisting of all of the debut authors that had been
nominated for the Center for Fiction First Novel Prize in the past three years
(2020, 2019, 2018) and did some analysis, based on... you guessed it, the
contents of their acknowledgements. In a perfect world, I could do this for
every single debut author, ever, but in practice I needed to limit the size of
the dataset and chose this particular group of ~80 writers because it seemed
like a somewhat representative cohort of fiction that I enjoy and that have also
enjoyed some level of acclaim (owing to the prize nomination and all.) Why debut
novelists you ask? Well, one, because that's what I'm working toward. But two,
technically speaking, it meant that writers would not be duplicated in the
dataset year over year (because, you're only a debut novelist once.) How
elegant!

Below, I'm dropping that knowledge, for the whole world (i.e. other people 
writing literary fiction and looking for agents) to enjoy. Answers to all your
most burning questions below, e.g.:

* Who should my agent be?
* What are the top MFAs/workshops/residencies?
* Is Alexander Chee really the most beloved writer in America?

Let's jump in!

```{r palettes, echo=FALSE}
# Color palettes: for this analysis we use Darjeeling1
wes_palettes <- list(
  BottleRocket1 = c("#A42820", "#5F5647", "#9B110E", "#3F5151", "#4E2A1E", "#550307", "#0C1707"),
  BottleRocket2 = c("#FAD510", "#CB2314", "#273046", "#354823", "#1E1E1E"),
  Rushmore1 = c("#E1BD6D", "#EABE94", "#0B775E", "#35274A" ,"#F2300F"),
  Rushmore = c("#E1BD6D", "#EABE94", "#0B775E", "#35274A" ,"#F2300F"),
  Royal1 = c("#899DA4", "#C93312", "#FAEFD1", "#DC863B"),
  Royal2 = c("#9A8822", "#F5CDB4", "#F8AFA8", "#FDDDA0", "#74A089"),
  Zissou1 = c("#3B9AB2", "#78B7C5", "#EBCC2A", "#E1AF00", "#F21A00"),
  Darjeeling1 = c("#FF0000", "#00A08A", "#F2AD00", "#F98400", "#5BBCD6"),
  Darjeeling2 = c("#ECCBAE", "#046C9A", "#D69C4E", "#ABDDDE", "#000000"),
  Chevalier1 = c("#446455", "#FDD262", "#D3DDDC", "#C7B19C"),
  FantasticFox1 = c("#DD8D29", "#E2D200", "#46ACC8", "#E58601", "#B40F20"),
  Moonrise1 = c("#F3DF6C", "#CEAB07", "#D5D5D3", "#24281A"),
  Moonrise2 = c("#798E87", "#C27D38", "#CCC591", "#29211F"),
  Moonrise3 = c("#85D4E3", "#F4B5BD", "#9C964A", "#CDC08C", "#FAD77B"),
  Cavalcanti1 = c("#D8B70A", "#02401B", "#A2A475", "#81A88D", "#972D15"),
  GrandBudapest1 = c("#F1BB7B", "#FD6467", "#5B1A18", "#D67236"),
  GrandBudapest2 = c("#E6A0C4", "#C6CDF7", "#D8A499", "#7294D4"),
  IsleofDogs1 = c("#9986A5", "#79402E", "#CCBA72", "#0F0D0E", "#D9D0D3", "#8D8680"),
  IsleofDogs2 = c("#EAD3BF", "#AA9486", "#B6854D", "#39312F", "#1C1718")
)

# If you need more colours than normally found in a palette, you
# can use a continuous palette to interpolate between existing
# colours:
# pal <- wes_palette(21, name = "Zissou1", type = "continuous")
wes_palette <- function(name, n, type = c("discrete", "continuous")) {
  type <- match.arg(type)
  
  pal <- wes_palettes[[name]]
  if (is.null(pal))
    stop("Palette not found.")
  
  if (missing(n)) {
    n <- length(pal)
  }
  
  if (type == "discrete" && n > length(pal)) {
    stop("Number of requested colors greater than what palette can offer")
  }
  
  out <- switch(type,
                continuous = grDevices::colorRampPalette(pal)(n),
                discrete = pal[1:n]
  )
  structure(out, class = "palette", name = name)
}
```

```{r data, echo=FALSE}
# Read in the data frame.
# https://docs.google.com/spreadsheets/d/1ZMf-UDG7AIarLH393TH7oKRzF-XkMN_qt5pVFz-8Hv4/edit?resourcekey=0-3Z9_rgI4qtmTyJMLZLcCDQ#gid=745766201
dedup <- read.csv("~/Downloads/Personal Project Acknowledgements - center for fiction.csv", na.strings = " ")

# Filter for just 2020
#dedup <- dedup[dedup$Year == 2020,]

# Format all of the strings in the acknowledgments field to exclude single quotes.
# We exclude these because if we leave them in it escapes the string and throws
# an error.
dedup$Text <- gsub("'", '', dedup$Text)

# Remove all the authors for whom we don't have any acknowledgment info (yet.)
dedup <- dedup %>% filter(Text != "")
```

```{r nlp, echo=FALSE}
# use NLPs NER annotator to identify person & location entities
sent_annot = Maxent_Sent_Token_Annotator()
word_annot = Maxent_Word_Token_Annotator()
org_annot <- Maxent_Entity_Annotator(kind = "organization") #annotate location
loc_annot = Maxent_Entity_Annotator(kind = "location") #annotate location
people_annot = Maxent_Entity_Annotator(kind = "person") #annotate person
```

```{r process, echo=FALSE}
# We want to create a data frame that stores both the thanker and the thankee
# for each set of acknowledgments. This requires us to loop through the original
# data frame extracting all of the names and appending the thankees with the name
# of the thanker.

# This will be a loop
# Make a list of the thankees for a single author
# The "text" variable is the Text field from each row of data
# This becomes the list of text_people which becomes the field called "thankee"
# The name of the author from the corresponding row is appended to each of the
# "thankees" in a column called "thanker"
# Repeat this operation for every row in the data frame

df_people <- data.frame()
df_orgs <- data.frame()

for (i in 1:nrow(dedup))
{
  text <- dedup[i,]$Text
  text = as.String(text)
  annot.l1 = NLP::annotate(text, list(sent_annot,word_annot,people_annot,org_annot))
  k <- sapply(annot.l1$features, `[[`, "kind")
  text_people = text[annot.l1[k == "person"]]
  text_orgs = text[annot.l1[k == "organization"]]
  
  if (length(text_people)>0) {
    df_1 <- as.data.frame(
      cbind(entity_1 = as.character(rep(dedup[i,]$Author,length(text_people))),
            entity_2 = text_people))
  } else {
    df_1 <- data.frame()
  }
  
  if (length(text_orgs)>0) {
    df_2 <- as.data.frame(
      cbind(entity_1 = as.character(rep(dedup[i,]$Author,length(text_orgs))),
            entity_2 = text_orgs))
  } else {
    df_2 <- data.frame()
  }
  
  df_people <- rbind(df_people, df_1)
  df_orgs <- rbind(df_orgs, df_2)
}

####
# Rename some entities that I know are wrong (manual operation)
####

# Format as character for string functions.
df_people$entity_2 <- as.character(df_people$entity_2)
df_orgs$entity_2 <- as.character(df_orgs$entity_2)

# Rename the entities
df_people[df_people$entity_2 == "Pam Zhang","entity_2"] <- "C Pam Zhang"
df_people[df_people$entity_2 %in% c("Lan Samantha Chang","Sam Chang"),"entity_2"] <- "Samantha Chang"
df_orgs[df_orgs$entity_2 == "ICM Partners","entity_2"] <- "ICM"

# Remove some entities
# Remove: School, University, Bath, MFA
remove_entities_orgs <- c("School", "University", "Bath", "MFA", "The")
df_orgs <- df_orgs[-which(df_orgs$entity_2 %in% remove_entities_orgs),]

#####
# Remove single names from people df (except for the most popular first name)
#####

# Determine the most thanked first name. Remove all other first name onlies.
calculate_mode <- function(x) {
  uniqx <- unique(na.omit(x))
  uniqx[which.max(tabulate(match(x, uniqx)))]
}

modal_name <- calculate_mode(df_people$entity_2)

df_people <- df_people[which(sapply(strsplit(df_people$entity_2, " "), length)>1 | 
                               df_people$entity_2 == modal_name),]

# Remove from the master list any person entity that is also the writer
# (entity_1)'s agent. (This is so that we only have writers connecting to
# agencies in the diagram and not writer > agent > agency which would be more
# cluttered.)

dedup <- dedup %>%
  mutate(author_agent_concat = paste(Author,Agent))

df_people <- df_people %>%
  mutate(author_agent_concat = paste(entity_1,entity_2))

df_people <- anti_join(df_people, dedup)

####
# Add some organizations that I know are missing (manual operation)
####

# Make a data frame with all of the authors + manual organizations
# Organization names (manual list because the model doesn't get literary orgs)
org_list <- c("Aspen Words", "Bread Loaf", "MacDowell", "Sewanee", "Tin House",
              "VONA", "Yaddo", "Whiting Foundation", "Civitella Ranieri",
              "PEN America", "Hedgebrook", "Millay", "Vermont Studio Center")

df_orgs_manual <- data.frame()

for (i in 1:length(org_list))
{
  df_3 <- dedup %>% filter(grepl(org_list[i], Text)) %>% select(Author)
  
  if (nrow(df_3)>0) {
    df_3 <- as.data.frame(
      cbind(entity_1 = as.character(df_3$Author),
            entity_2 = as.character(rep(org_list[i],length(df_3$Author)))))
  } else {
    df_3 <- data.frame()
  }
  
  df_orgs_manual <- rbind(df_orgs_manual, df_3)
}

df_orgs <- rbind(df_orgs, df_orgs_manual)

# Remove agencies from orgs df. Remove from the list any org entity that is also
# the writer's agency. (We will add agencies back later.)
dedup <- dedup %>%
  mutate(author_agency_concat = paste(Author,Agency))

df_orgs <- df_orgs %>%
  mutate(author_agency_concat = paste(entity_1,entity_2))

df_orgs <- anti_join(df_orgs, dedup)

# Join all three tables to make one master table:
# This includes the people table (with agents excluded) and
# the orgs table (with manual orgs added and agencies stripped out)
df_total <- rbind(df_people[c("entity_1","entity_2")], 
                  df_orgs[c("entity_1","entity_2")])

# Remove all duplicate rows (we just want one match per entity pair.)
df_total <- unique(df_total)

####
# Make a list of all the entities to include in the network.
# Remove all rows in which entity_2 is not duplicated (i.e. an entity who was
# acknowledged by only one writer, in which case we don't consider them a
# member of the network)
####

# Make the list: every single entity that appears as a thanker or a thankee
df_total_e1 <- data.frame(entity = df_total[,"entity_1"])
df_total_e2 <- data.frame(entity = df_total[,"entity_2"])
df_total_include <- rbind(df_total_e1, df_total_e2)

df_total_include <- as.vector(
  df_total_include[df_total_include$entity %in% 
                     names(which(table(df_total_include$entity) > 1)), ])

# Select only the entity_2s from df_total that are also in the list of 
# df_total_includes
df_total <- df_total %>% filter(entity_2 %in% df_total_include)

# Make a data frame with all of the authors + agencies: i.e. add back the
# agencies to the completed dataset (we treat these differently than other
# entities, because if a writer is the only entity_1 associated with an agency
# we still want to include it, i.e. it doesn't need to satisfy the > 1 filter.
df_agency <- data.frame(entity_1 = dedup[,"Author"],
                        entity_2 = dedup[,"Agency"])

# Make a data frame with all of the authors + MFA programs: same logic as above
# TODO(remove the org entities from entity_2 that match the MFA in the remove
# agencies step)
df_mfa <- data.frame(entity_1 = dedup[,"Author"],
                     entity_2 = dedup[,"MFA"])

# Add the agency and MFA data frames to the person / org data frame. (Remember
# that we are doing this at the end to ensure that when a writer is the only
# person represented by their agency, the agency still appears in the network.)
df_total <- rbind(df_total[c("entity_1","entity_2")], 
                  df_agency[c("entity_1","entity_2")],
                  df_mfa[c("entity_1","entity_2")]
                  )

# Manually inspect the data frame in google sheets.
# write.csv(df_total,"~/Downloads/publishing_data_export.csv")
# df_total <- read.csv("~/Downloads/publishing data manual cleanup - publishing_data_export.csv")

# Remove rows with empty connections
df_total <- df_total[df_total$entity_2 != "",]
```
> Who's in the acknowledgements?

There are a few different types of entities that writers typically acknowledge:

* agents / agencies
* editors / publishing houses
* MFA programs
* Workshops / retreats / foundations
* Friends and family

For the purposes of this analysis I've organized these entities into three 
broader categories: agencies, organizations, and individuals. The charts below highlight the entities (agencies, organizations, and individuals) that were
shouted out the most by the debut authors.

If we look across all entities we see a mix of agencies and organizations on the
leaderboard. You'll notice only one individual make the top ten overall list.
That individual is none other than... **Katie!** 

I know, I know, there are lots of Katies out there supporting the arts, but... it's really hard to get into Bread Loaf or Tin House. Finding a Katie to stan my work, though? Feels more doable.

*Note: now feels like a good time to mention that this analysis was inspired by Richard Jean So's [work in the New York Times](https://www.nytimes.com/interactive/2020/12/11/opinion/culture/diversity-publishing-industry.html) on race in publishing. I've always dreamed of the day
that someone would successfully "Moneyball literature" and while that's not
exactly what he's doing, I really admire the use of data and analytics to
understand books and book publishing. Although my analysis does not directly
deal with race, some of my conclusions are related. Namely that the social
networks of award nominated writers are quite compact (more on that below)
and—related to the Katie point—succeeding in the literary fiction game requires
the support of white people and institutions. (80% of people named Katie are
white, and 80% of agents and editors are white.)*

```{r most_thanked, include = FALSE}
df_most_thanked_entities <- df_total %>%
  group_by(entity_2) %>%
  summarise(cnt = n()) %>%
  top_n(10)

# Cheat a little bit and add all the Katies (or whatever the modal name is)
df_most_thanked_entities[df_most_thanked_entities$entity_2 == modal_name,]$cnt <-
  length(unique(df_people[df_people$entity_2 %like% modal_name,"entity_1"]))

# Colors for bar chart
most_thanked_entities_palette <- wes_palette(nrow(df_most_thanked_entities),
                                             name = "Darjeeling1", 
                                             type = "continuous")

# Plot
p1 <- df_most_thanked_entities %>%
  ggplot(aes(x = reorder(entity_2, cnt), y = cnt, fill = entity_2, label = cnt)) +
  geom_bar(stat = "identity") +
  coord_flip() +
  theme_light() +
  scale_fill_manual(values=most_thanked_entities_palette) +
  theme(legend.position = "none",
        axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank(),
        axis.title.y=element_blank(),
        axis.ticks.y=element_blank(),
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        panel.border = element_blank(),
        axis.line = element_blank()) +
  labs(subtitle="Overall")

df_most_thanked_agencies <- df_total %>%
  filter(entity_2 %in% df_agency$entity_2) %>%
  group_by(entity_2) %>%
  summarise(cnt = n()) %>%
  top_n(10)

# Colors for bar chart
most_thanked_agencies_palette <- wes_palette(nrow(df_most_thanked_agencies), 
                                             name = "Darjeeling1", 
                                             type = "continuous")

# Plot
p2 <- df_most_thanked_agencies %>%
  ggplot(aes(x = reorder(entity_2, cnt), y = cnt, fill = entity_2, label = cnt)) +
  geom_bar(stat = "identity") +
  coord_flip() +
  theme_light() +
  scale_fill_manual(values=most_thanked_agencies_palette) +
  theme(legend.position = "none",
        axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank(),
        axis.title.y=element_blank(),
        axis.ticks.y=element_blank(),
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        panel.border = element_blank(),
        axis.line = element_blank()) +
  labs(subtitle="Agencies")

df_most_thanked_persons <- df_total %>%
  filter(entity_2 %in% df_people$entity_2 
         & !(entity_2 %in% df_orgs$entity_2)
         & !(entity_2 %in% df_orgs_manual$entity_2)
         & !(entity_2 %in% df_agency$entity_2)) %>%
  group_by(entity_2) %>%
  summarise(cnt = n()) %>%
  top_n(10)

# Do the modal name fix
# Cheat a little again to make sure that first, last modal names get counted with
# first only modal names
# Calculate total number of modal names (done already)
# Remove all modal names from the df
# Add a new modal name row with the total modal names
#df_most_thanked_persons[!(df_most_thanked_persons$entity_2 %like% modal_name),]
#df_most_thanked_persons <- rbind(df_most_thanked_persons, 
#                                 data.frame(entity_2 = modal_name,  cnt =
#  length(unique(df_people[df_people$entity_2 %like% modal_name,"entity_1"]))))

# Colors for bar chart
most_thanked_persons_palette <- wes_palette(nrow(df_most_thanked_persons), 
                                            name = "Darjeeling1", 
                                            type = "continuous")

# Plot
p3 <- df_most_thanked_persons %>%
  ggplot(aes(x = reorder(entity_2, cnt), y = cnt, fill = entity_2, label = cnt)) +
  geom_bar(stat = "identity") +
  coord_flip() +
  theme_light() +
  scale_fill_manual(values=most_thanked_persons_palette) +
  theme(legend.position = "none",
        axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank(),
        axis.title.y=element_blank(),
        axis.ticks.y=element_blank(),
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        panel.border = element_blank(),
        axis.line = element_blank()) +
  labs(subtitle="Individuals")

p4 <- egg::ggarrange(p2,p3, ncol = 1, heights=c(
  nrow(df_most_thanked_agencies),
  nrow(df_most_thanked_persons)))
```

**Most acknowledged:**

``` {r acknowledgement_plots, echo = FALSE}
#title1=text_grob("Most acknowledged:", size = 15, face = "bold", x = 0, hjust = 0)
grid.arrange(p1, p4, ncol=2)#, top=title1)
```

> How many people does it take to write a novel?

We looked at who's getting shoutouts, now let's look at how many shoutouts our
debut authors are giving. Below is the distribution of the number of entities
thanked across all of our authors. So how big a village does it take to write a
novel?

Most debut novelists acknowledge 29 people or more -- call it 30 if we include
the author who... probably did the most work?

The minimum number of entities acknowledged is... 0. (Whomp whomp whomp.) And
the maximum is a much more bustling village of 88.

**Distribution of number and length of acknowledgements:**

```{r n_entities_thanked, ,fig.height=3, fig.width=5, echo = FALSE}
# Number of entities acknowledged.
df_people_thanked <- as.data.frame(df_people %>% group_by(entity_1) %>% summarise(cnt = n()))
df_orgs_thanked <- as.data.frame(df_orgs %>% group_by(entity_1) %>% summarise(cnt = n()))
df_total_thanked <- left_join(df_people_thanked, df_orgs_thanked, by = c("entity_1" = "entity_1")) %>%
  mutate(total_thanked = cnt.x + cnt.y)
df_total_thanked[is.na(df_total_thanked)] <- 0

p5 <- ggplot(df_total_thanked[df_total_thanked$total_thanked <= 80,], aes(x=total_thanked)) + 
  geom_histogram(binwidth=10, fill="#00A08A", color="#e9ecef", alpha=0.9) +
  theme(legend.position = "none",
        axis.ticks.x=element_blank(),
        axis.title.x=element_blank(),
        axis.text.y=element_blank(),
        axis.title.y=element_blank(),
        axis.ticks.y=element_blank(),
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        panel.border = element_blank(),
        axis.line = element_blank()) +
  scale_x_continuous(breaks = seq(0,80, 10)) +
  labs(subtitle = "Number of Acknowledgements")

# Number of words in the acknowledgements.
p6 <- ggplot(dedup, aes(x=Word.count)) + 
  geom_histogram(binwidth=1000,fill="#00A08A", color="#e9ecef", alpha=0.9) +
  theme(legend.position = "none",
        axis.ticks.x=element_blank(),
        axis.title.x=element_blank(),
        axis.text.y=element_blank(),
        axis.title.y=element_blank(),
        axis.ticks.y=element_blank(),
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        panel.border = element_blank(),
        axis.line = element_blank()) +
  scale_x_continuous(breaks = seq(0, 8000, 1000)) +
  labs(subtitle = "Word Count of Acknowledgements")

ggarrange(p5, p6, ncol = 1)
```

```{r graph_analysis, echo = FALSE}
####
# Generate a directed igraph object in order to calculate the degree for each
# entity being thanked.
####
# Turn data frame into a directed igraph object.
g_for_deg <- graph_from_data_frame(d=df_total[c("entity_1","entity_2")], directed=T)

# Calculate the degree for each node where the entity is the one being thanked:
deg <- degree(g_for_deg, mode="in")

####
# Generate an undirected igraph object to build the network.
####
# Turn data frame into an undirected igraph object.
g <- graph_from_data_frame(d=df_total[c("entity_1","entity_2")], directed=F)

# Assign each entity to a community
clp <- cluster_label_prop(g)
#https://igraph.org/r/doc/cluster_edge_betweenness.html
ceg <- cluster_edge_betweenness(g)
```

> But, like, do they all have fancy MFAs and exclusive residencies? Are all
these award winning debut novelists best friends? Because it kind of seems like
they are on Twitter...

This was the question that was really gnawing at me when I started this whole
exercise. As a fairly avid reader of novel acknowledgements I see the same
names over and over again, which leads me to believe that novel publishing is a
super exclusive closed circuit that no mere mortal can simply enter at will. But
then again... I do have an active imagination (I am writer after all!) so I
wanted to put my intuition to the test.

To do that I created a social graph based on the debut novelist's
acknowledgements section. I used a natural language processing model to extract
all of the named entities from the text of each author's acknowledgements. There
are two major limitations with this approach which I will call out now:

* Just because someone isn't acknowledged by a writer doesn't mean that person
isn't in that writer's social network.
* Our natural language processing model isn't perfect so sometimes it
  + Miscategorizes entities (e.g. assumes Sewanee is a place not an organization)
  + Doesn't fully recognize entities (e.g. Iowa is distinct from University of
  Iowa)
  
The second problem is easier to address than the first, so I did try to clean 
the data manually a bit, but it probably still isn't perfect. (e.g. Curtis Brown
is actually an organization but may be labeled as an individual.) But I think
it's good enough for government work. The first problem is kind of a
philosophical one and I'm just going to assert here that if a writer didn't
acknowledge an entity in the approximately 2,500 words the average author 
allocated to their acknowledgements that entity is not in that writer's inner
circle.

Now onto the graph.

It's color coded based on whether the entity is a:

* debut author
* agency
* other organization (e.g. workshop, residency, MFA program)
* an individual / friend

The bigger the bubble and the more central the bubble is in the chart the 
more important that bubble is to the social network. So the biggest bubble 
(Bread Loaf) represents the node in the network that is most central.

You can click on the bubbles to see what other entities they are connected to.
You can also drag the bubbles around to see what amount of force they exert on
the network. (The more the network moves with the bubble, the bigger its
influence.)

*Note: I did not check my work, however I did watch a conversation between Lucy
Tan and Susie Yang hosted by everyone's favorite Brooklyn bookstore Books Are
Magic in which they revealed a long-standing friendship, so the fact that they
show up so close together in the graph is... super vindicating.*

**Social network of 80 award nominated debut authors:**

``` {r forcenetwork, out.width="100%", out.height="800px", echo = FALSE}
#Convert igraph object to networkD3 object
g_d3 <- igraph_to_networkD3(g)
df_nodes <- g_d3$nodes
df_links <- g_d3$links

# Add grouping variable to the nodes list
df_nodes <- df_nodes %>%
  mutate(group =
           ifelse(name %in% dedup$Author, "Debut Author",
                  ifelse(name %in% df_agency$entity_2, "Agency",
                         ifelse(name %in% df_orgs$entity_2, "Organization",
                                "Individual"))))

# Make a JS readable color scale to distinguish among the different groups 
# (based on our Darjeeling1 Wes Anderson palette)
ColourScale <- 'd3.scaleOrdinal()
            .domain(["Debut Author", "Agency", "Organization", "Individual"])
           .range(["#FF0000", "#F2AD00", "#00A08A", "#5BBCD6"]);'

# Add in the degreeness for each entity to determine the bubble size
df_deg <- tibble::rownames_to_column(data.frame(deg), "name")
df_nodes <- left_join(df_nodes, df_deg)

# Scale up the degreeness factor so that the circles are bigger and easier to
# views.
df_nodes <- df_nodes %>% mutate(deg = deg^3)

# Final force network
forceNetwork(Links = df_links, Nodes = df_nodes,
             Source = 'source', 
             Target = 'target', 
             NodeID = 'name',
             Group = 'group',
             linkColour = "FFFFFF",
             Nodesize = 3,
             fontSize=10,
             legend=T,
             opacity = .8,
             bounded = F,
             opacityNoHover = .4,
             #charge = -10,
             colourScale = JS(ColourScale))
```

> Cool bubbles bro, but can we actually make sense of the social graph?

The treemap below segments each of the entities into different communities. The
communities are based on propagating labels, which is a fast, nearly linear time
algorithm for detecting community structure in networks. In works by labeling
the vertices with unique labels and then updating the labels by majority voting
in the neighborhood of the vertex.

In other words, the communities represent the entities that are in the same
"neighborhood." From this we can start to understand the social networks within
the network.

Click on a community to take a closer look at the other entities in their
community. As with the social graph, the sizes of each quadrilateral in the map
represent the influence of the entity.

``` {r treemap_prep, echo = FALSE}
# Create a new data frame with all of the nodes plus the community they belon
# to
#df_nodes_tm <- cbind(df_nodes, data.frame(community = clp$membership))
df_nodes_tm <- cbind(df_nodes, data.frame(community = ceg$membership))
df_nodes_tm <- df_nodes_tm[,c("name","group","deg","community")]
# Rename the columns so that they match the js requirement for highcharter
names(df_nodes_tm) <- c("name", "group", "value", "parent")
#Reorder just in case that's what's causing the error
df_nodes_tm <- df_nodes_tm[c("name", "parent", "value", "group")]
# Make everything except the value a character
df_nodes_tm$parent <- as.character(df_nodes_tm$parent)
# Make the df into a list
df_nodes_list <- lapply(split(df_nodes_tm,df_nodes_tm$name), function(x) as.list(x))
# Make a parent list (just convert a data frame into a list to make life easier)
df_nodes_parent <- data.frame(id = unique(df_nodes_tm$parent),
                   name = unique(df_nodes_tm$parent),
                   color = as.vector(wes_palette(length(unique(df_nodes_tm$parent)),
                                                         name = "Darjeeling1", 
                                                         type = "continuous")))
# Make everything a character
df_nodes_parent$name <- as.character(df_nodes_parent$name)
df_nodes_parent$id <- as.character(df_nodes_parent$id)
df_nodes_parent$color <- as.character(df_nodes_parent$color)

# Make a parent list and join it to the rest of the nodes list
df_nodes_parent_list <- lapply(split(df_nodes_parent,df_nodes_parent$id), function(x) as.list(x))
df_nodes_list <- c(df_nodes_parent_list, df_nodes_list)

# Unname the list FOR SOME REASON WITH NAMES YOU GET A BIG ERROR (DOH!)
df_nodes_list <- unname(df_nodes_list)
```

**Treemap of 80 debut authors and their social networks:**
``` {r treemap_visual, out.width="100%", out.height="800px", echo = FALSE}
highcharter::highchart() %>% 
  highcharter::hc_add_series(
    type = "treemap",
    layoutAlgorithm = "squarified",
    allowDrillToNode = TRUE,
    tooltip = list(pointFormat = "Name: {point.name} 
                   <br/>Degree: {point.value}
                   <br/>Community: {point.parent}"),
    levels = list(
      list(
        level = 1,
        dataLabels = list(
          enabled = FALSE
        )
      ),
      list(
        level = 2,
        dataLabels = list(
          enabled = TRUE
        )
      )
    ),
    data = df_nodes_list
  )
```

**Breaking it down: the 8 types of writing communities**
<p><small>*Inspired by FiveThirtyEight's ["Hollywood Taxonomy."](https://fivethirtyeight.com/tag/hollywood-taxonomy/)*</small></p>

## <span style="color: #CC201B;">The Road Not Taken</span>

*Two roads diverged in a wood, and I— I took the one less traveled by, And that
has made all the difference.<br/>—Robert Frost*

**Member Entities**: Bread Loaf, HG Literary, New York Foundation for the Arts, Hunter
College, David Shulman, Lisa Keim, Peter Carey, Sean McDonald, Levine Greenberg
Rostan

It's with some irony that I've labeled this community after that famous Robert
Frost poem. First, because the entity with the most influence in this community
is Bread Loaf, which is also the entity with the most influence across the
entire social network, and therefore probably better described as the road
*taken.* However, for you literature buffs out there, you know that Frost's
poem is famously misinterpreted (it's not strictly about 'doing your own thang')
and so I thought this would be an appropriate twist. Oh yeah, also (according
to Wikipedia) Bread Loaf's inception was closely associated with Robert Frost
who lived nearby and attended a total of 29 sessions.

## <span style="color: #FF0000;">The Marriage Plot</span>

*To start with, look at all the books.<br/>—Jeffrey Eugenides*

**Member Entities**: Tin House, Sewanee, Rebecca Makkai, William Morris Endeavor, Aevitas Creative Management, Darin Straus, Jeffrey Eugenides, Jill Bialowsky, 
Nicholas Latimer, Julia Phillips, Norton

Obviously Jeffrey Eugenides (author of The Marriage Plot) is in the community. 
But a "marriage plot" also refers to a novel form popularized by such illustrious
names in English literature as Jane Austen, George Eliot and the Bronte sisters.
Seemed mostly fitting for a community comprised of literary stalwarts like Tin
House, Sewanee and WME.

## <span style="color: #1C8E7A;">Lan Samantha Chang stans</span>

*[Poets] are the canaries in the mineshaft of our existence.<br/>—Lan Samantha 
Chang*

**Member Entities**: University of Iowa, Ethan Canin, Lan Samantha Chang,
DeFiore and Company, Marilynne Robinson, Molly Stern, Rachel Rokicki, Amanda
Dennis, Charlie D'Ambrosio, Mia Bailey, Drew Calvert, Noel Carver

Okay, so technically this is the "Iowa" community, but I couldn't resist a plug
for Sam Chang, who I was lucky enough to meet in a workshop last summer, and who
is just the bees knees. Is anyone surprised that the most renowned creative
writing program in the country is run by someone everyone loves?

## <span style="color: #8D473D;">MFA + NYC</span>

*The MFA has many detractors, and many of them greatly overstate their case, 
harking back to a time when every writer was a wine-chugging Hemingway firing a 
homemade rifle at a rabid shark from the back of a speeding ambulance.<br/>—Chad 
Harbach*

**Member Entities**: Columbia University, ICM, Katie, Hedgebrook, Curtis Brown, John
Freeman, Luis Alberto Urrea, Rona Jaffe Foundation, VONA, Dennis Norris II,
Georges Borschardt, Helen Garnons-Williams, Jessica Williams

There's an ongoing debate in the literary community: MFA or NYC. In other words,
where should a writer cut their teeth. The consensus turns out to be: both. And
the beauty of this community is that the big boy at the center (Columbia
University) is both MFA and NYC. Who said writers can't have it all!

## <span style="color: #50A45C;">Alexander Chee and Artists' Colonies</span>

*...the only things you must have to become a writer are the stamina to continue and a wily, cagey heart in the face of extremity, failure and success.<br/>—Alexander Chee*

**Member Entities**: MacDowell, Alexander Chee, Aragi, Inc., Trident Media Group, Yaddo, Andra Miller, NYU, Michelle Koufopolous, University of New Mexico

If you spend like five seconds on literary Twitter you will encounter this name:
Alexander Chee. Seriously, from where I sit, he seems like the Tom Cruise (the 
Harry Styles? the Timothee Chalamet? I don't know celebrities) of the literary community. He's a BIG DEAL. So are certain artists' colonies, like MacDowell and Yaddo, which you can read about, but are basically cabin in the woods type
situations where only the best, most talented writers are invited to stay and
take their lunch in hand-delivered picnic baskets.

## <span style="color: #F69100;">That National Book Award Energy</span>

*Books matter.<br/>—Lisa Lucas*

**Member Entities**: Janklow & Nesbit, Vermont Studio Center, Center for Fiction, Chris Jackson, Megan Lynch, Michael Taeckens, Rachel Kushner, Writers House, School of the Art Institute of Chicago, University of New Orleans

As a lay person I couldn't immediately come up with a unifying theory for this
community so I did a bit of Googling. Something seemed to unite many of them
(i.e. was in their bios and on their home pages) was the National Book Award. Be
friends with these people if you want to win the big one!

## <span style="color: #F3A300;">Random House</span>

*If there is a book that you want to read, but it hasn't been written yet, you must be the one to write it.<br/>—Toni Morrison*

**Member Entities**: Random House, Susan Kamil, Andrea Walker, Andy Ward, Avideh Bashirrad, Emma Caruso, Leigh Merchant, Toni Morrison

I could have come up with a cute label for this community, but didn't. This is
Random House and friends, including Toni Morrison, who is one of the greats, and
who will no doubt still be getting shout outs long, long after she's gone.

## <span style="color: #32806E;">Maxwell Perkins, etc.</span>

*Your manuscript is both good and original, but the part that is good is not original, and the part that is original is not good.<br/>–Samuel Johnson*

**Member Entities**: Cal Morgan, The Clegg Agency, Deb Seager, Katie Raissian, James Nolan, Morgan Entrekin, Judy Hottensen, University of Texas, George Mason University, The Cheney Agency

So the energy in this community leaned editorial, hence the nod to Maxwell
Perkins, the most famous editor of all time. Supposedly he discovered Hemingway,
Fitzgerald and Wolfe, which is quite a contribution to American letters. (He
probably spent a lot of time in bars. Lol, jk.)

```{r tweet-from-dsquintana}
#tweet_screenshot(
#  tweet_url("alexpghayes", "1211748406730706944")
#)

#include_tweet("https://twitter.com/dsquintana/status/1275705042385940480")
```

> So... which agency?

If you recall, the genesis of this entire project was hunting for literary
agents in the acknowledgements section of debut novels. After all of this, a
reasonable person might wonder: did you pick an agent? Essentially, yes. For the
purposes of this analysis I looked at agencies not individual agents, because
they were easier to keep track of. (If I were doing this for real, I'd certainly
want to look at individual agents, but that's for another day.)

How did I decide? Check out the chart below. I made a scatter plot comparing the
total number of award nominated debut authors represented by the agency compared
to the "centrality" score for the agency (i.e. the measure of influence of the
agency.) Representing more authors is obviously a good sign (although it could
equally be a sign that the agency itself represents more authors overall, aka is
big), but for me personally, I thought that being less central / influential
would also be a positive. As in, the less central the agency was (the less in
the "scene" it was) the more likely it would be to represent someone such as
myself, i.e. a random person who is decidedly not in the "scene."

So here's what I did. I added a regression line, with error bounds to a
scatter plot of # authors vs centrality score. The regression line (the blue
line) tells us that the more central the agency is the more award winning
debut authors it represents (or vice versa, the more award winning debut authors
the agency represents the more central it is.) This is intuitive! But where
things get interesting is when we look at agencies outside of the boundary.
Agencies below the boundary are more central than the number of award winning
debut authors. In other words, given how influential they are we would expect
them to represent more of these debut authors. Agencies above the boundary on 
the other hand represent more authors than you would expect given how central
they are. Which means? These agencies (HG Literary, DeFiore and Company and ICM)
are disproportionately good at picking random, talented writers to represent (of
which I consider myself one.)

Hover over the point to reveal the name of the agency. The agencies that are
labeled are the ones that seem to be successfully taking chances on "unknown
kids," so to speak.

**Scatterplot of agencies by # of authors represented vs centrality score:**
``` {r agent_selection, echo = FALSE}
# Calculate a centrality score for each entity.
ec <- eigen_centrality(g)
#ec$vector

# Create a data frame with just the agencies including their centrality scores.
agency_chart <- cbind(df_nodes, cen = ec$vector)
agency_chart <- agency_chart[agency_chart$group == "Agency",]

# Count the number of authors that each agency represents.
agency_reps <- dedup %>%
  group_by(Agency) %>%
  summarise(cnt = n())

# Create a df for a scatter plot of number of authors repped and centrality.
agency_scatter <- left_join(agency_chart, agency_reps, by = c("name" = "Agency"))

#agency_scatter$cen_log <- log(agency_scatter$cen)

# Plot the scatter.
plot <- ggplot(agency_scatter[agency_scatter$cnt > 1,], aes(x=cen, y=cnt, label = name)) +
  geom_point(size = 5, aes(colour = factor(name))) +
  geom_text(
    aes(label=ifelse(name %in% c("ICM","DeFiore and Company","HG Literary"),
                     as.character(name),'')), size=3) +
  geom_smooth(method='lm') +
  theme_minimal() +
  theme(
    axis.text.x = element_blank(),
    axis.text.y = element_blank(),
    panel.grid.major = element_blank(), 
    panel.grid.minor = element_blank(),
    panel.background = element_blank(),
    legend.position = "none") +
  scale_color_manual(values = wes_palette(n=length(agency_scatter[agency_scatter$cnt > 1,]$name),
                                          name = "Darjeeling1",
                                          type = "continuous")) +
  ylab("# of Debut Authors Represented") + xlab("Agency 'Centrality' Score")

# Use plotly to make the plot interactive (tooltips.)
ggplotly(plot, tooltip = "label")  %>% 
  config(displayModeBar = FALSE) %>%
  onRender("function(el, x) {Plotly.d3.select('.cursor-crosshair').style('cursor', 'default')}")
```

> One more thing: the hot mess fallacy

The number one curiosity for me re: writers and agents and writers and editors is
the mysterious alchemy of transforming a manuscript into something publication
ready. The way they tell it, you can only secure an agent if you send them the 
best, most polished, most perfect novel and anything less is a waste
of your time and theirs. At the same time, a quick glance through the
acknowledgements tells... a different story. The way authors talk, they
walked up to their agents / editors with a hot piece of garbage which was duly 
transformed. Is this just writerly self-effacement? Or something else? Any
writers out there will to share the manuscript they first sent their agent so we
can compare it to what was published? (Don't all jump up at once.)

Until that happens, I expect it will remain a mystery. In the mean time, a
sample of some unattributed acknowledgements so you know what I'm referring to.

**A sample of acknowledgements that make it seem like the novel may not have been
complete before the author found representation `r emo::ji("thinking")`:**

------

<p style="font-family: times, serif; font-size:14pt; font-style:italic">
    "To the amazing [Agent] who saw this novel's potential
long, long before I did and who tirelessly guided me in every step of the journey."<br/>–A writer
</p>

------

<p style="font-family: times, serif; font-size:14pt; font-style:italic">
"I owe a thousand thanks also to [Agent], who fell in love
with this book so many years ago and stayed with it until it was ready to be
brought out into the world."<br/>–Another writer
</p>

------

<p style="font-family: times, serif; font-size:14pt; font-style:italic">
"[To] my agent, without whose intervention I would have kept rewriting the same five chapters of this book forever."<br/>–Yet another writer
</p>

------

<p style="font-family: times, serif; font-size:14pt; font-style:italic">
"[To] my editor, who polished this story until it shone."<br/>–Yet another writer
still
</p>

------

<p style="font-family: times, serif; font-size:14pt; font-style:italic">
"[To] my agent, who believed in this book, and in me, long before I did. I would never have finished without you."<br/>–A different writer
</p>

------

<p style="font-family: times, serif; font-size:14pt; font-style:italic">
"Were it not for [Agent], this book would be a pile of Post-its and I an incoherent shell."<br/>–Someone else
</p>

------

<p style="font-family: times, serif; font-size:14pt; font-style:italic">
"My agent cheered me on from the moment I first mentioned the idea."<br/>
–Another writer
</p>

------

<p style="font-family: times, serif; font-size:14pt; font-style:italic">
"In [Agent's] first editorial letter, she wrote that the draft had many beautiful moments, but “needs some serious work." In other words, as she later told me: I
needed to rewrite the whole thing."<br/>–Different guy
</p>

------

<p style="font-family: times, serif; font-size:14pt; font-style:italic">
"[To Agent], for taking me on, for revising the entire manuscript three times."
<br/>–Three times!
</p>

------

<p style="font-family: times, serif; font-size:14pt; font-style:italic">
"[Agent]: dear friend, vital first reader, and agent extraordinaire, who
believed in this book before it existed."<br/>–You get the idea
</p>

> Final conclusions

I feel like I learned a lot here. Roughly the equivalent of trawling Twitter
for... many weeks. How about you? Any questions, comments or feedback? Anything I 
should add or subtract? (Let me know in the comments! Send me a like. Smash
that subscribe button, etc. etc. Just kidding. I'm old fashioned. You can 
<a href="mailto:cer1029@gmail.com">shoot me an email</a>.)
